Building a framework to perform automated verification of solar photovoltaic off-grid systems

### 2018-10-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r1.tex
updated abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with emphasis to solar photovoltaic systems. Electrification of rural areas can improve the standard of education, health conditions, and living of this population. In addition, depending on the geography of the country, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension. Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects. This paper aims to build the framework to apply automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective. Results show that the proposed tool can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same fail. Data from practical application of solar systems prove the results obtained by the tool.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
With declining costs and increasing performance, the deployment of renewable energy in off-grid systems is growing in both developed and developing countries, with particular emphasis on solar photovoltaic systems. Electrification of rural areas can improve the education standard, health conditions, and also the life of this population. In addition, depending on the country geography, using renewable energy sources in off-grid mode is a feasible solution if compared to grid extension. Tools to aid the design and validation of rural electrification projects are available; however, there is no software that applies formal verification to evaluate rural electrification projects. This paper aims to build a framework to apply an automated verification method to mathematical models of a solar photovoltaic system to validate its design from a formal verification perspective. Experimental results show that the proposed approach can find situations where the sized solar photovoltaic system fails to met the requirements demanded to electrify a house, and that simulation made with commercial tools can not find the same failure. Data from practical application of solar systems prove the results obtained by the proposed approach.
\end{abstract}
